Constraints on the mass and occupation fraction of dark matter halos hosting Lyman-alpha emitters at $z\sim 3$

### 2013-06-27 paper/ms.tex
little spelling corrections on paper

Abundance matching methods throughout cosmic time from redshifts
$0<z<8$ \cite{Behroozi2013a,Behroozi2013b} work based on observational
results for Lyman Break Galaxies. In thos studies the minimum halo
mass considered to be relevant in their analysis is
$10^{11.4}$\hMsun. For that mass, \cite{Behroozi2013a} report a
stellar mass mass around $(1.0\pm0.3)\times 10^{9.0}$
\hMsun, while their star formation rate is in the range $0.6\pm 0.2$
Msun yr$^{-1}$, which nevertheless are close to the lower bound of
values inferred for LAEs at high redshift
\citep{Gawiser2007,Nilsson2009,Pentericci2009}.

In our results, all the preferred models have a halo mass range lower
than the minimum of $M_{\rm min}<10^{11.4}$\hMsun considerend in
abundance matching at $z=3$. This mass scale is also strictly superior to
the great majority of  $M_{\rm max}$ values allowed in the models with
low escape fraction.   This suggests that a detailed and careful study
of the s ectral and photometric properties of LAEs coupled to the kind
of analysis performed in this paper can be a guide in the study of the
properties of low mass dark matter halos at $z=3.1$, extending the
capabilities of abundance matching methods.

>>>>

Abundance matching methods throughout cosmic time from redshifts
$0<z<8$ \cite{Behroozi2013a,Behroozi2013b} work based on observational
results for Lyman Break Galaxies. In those studies the minimum halo
mass considered to be relevant in their analysis is
$10^{11.4}$\hMsun. For that mass, \cite{Behroozi2013a} report a
stellar mass mass around $(1.0\pm0.3)\times 10^{9.0}$
\hMsun, while their star formation rate is in the range $0.6\pm 0.2$
Msun yr$^{-1}$, which nevertheless are close to the lower bound of
values inferred for LAEs at high redshift
\citep{Gawiser2007,Nilsson2009,Pentericci2009}.

In our results, all the preferred models have a halo mass range lower
than the minimum of $M_{\rm min}<10^{11.4}$\hMsun considerend in
abundance matching at $z=3$. This mass scale is also strictly superior to
the great majority of  $M_{\rm max}$ values allowed in the models with
low escape fraction.   This suggests that a detailed and careful study
of the spectral and photometric properties of LAEs coupled to the kind
of analysis performed in this paper can be a guide in the study of the
properties of low mass dark matter halos at $z=3.1$, extending the
capabilities of abundance matching methods.
